### 2016-06-29 GPCE2016/sections/CaseStudy.tex
author-info & revise.
recovered and edited marco text in S3 and S4

Smalltalk and Dart offer method cascading~[??];
at the price of introducing additional syntax,
this avoid the need for fluent setters;
method cascading (as setters in general) 
intrinsically rely  on an imperative setting.
Our approach supports both fluent setters and (functional) 
fluent withers.

>>>>

Smalltalk and Dart offer method cascading and avoid the need for fluent setters.
It is achieved at the price of introducing additional syntax and 
intrinsically relies on an imperative setting. 
Our approach supports both fluent setters and (functional) 
fluent withers.

### 2016-06-29 GPCE2016/sections/Overview.tex
recovered and edited marco text in S3 and S4

% \paragraph{Property updater as Injections}

% By declaring fields in Newspeak and other languages,
% the programmers specifies field signatures and (critically) the intention of storing such information. Then the language generate getter and setter.
% Once state is abstracted away,
% it is well known that is possible to replace state
% access with computation, but the type of the field stays the same.

% Our fluid approach to state is specular:
% the intention of storing the information is not expressed by the programmer and set in stone, 
% but can vary by inheritance:
% We generate the idea of the field
% just starting from getters and setters signatures.

% In this case, we leverage on our fluid state to changing the underling type of the field,
%  and our \Q@with@ is providing
% the right injection from the old type to the new one.

>>>>

\paragraph{Property updater as Injections}

By declaring fields in Newspeak and other languages,
the programmers specifies field signatures and (critically) the intention of storing such information. 
Then the language generates getters and setters.
Once state is abstracted away, it is well known that state
access can be replaced with computation, but the type of the field stays the same.
% Our fluid approach to state is specular:
In our approach,
the intention of storing the information is not expressed by the programmer and set in stone, 
but can vary by inheritance: we generate the idea of the field
just starting from signatures of getters and setters.
In this case, we leverage on our fluid state to changing the underling type of the field,
 and our \Q@with@ provides the right injection from the old type to the new.
